---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# merc

<!-- badges: start -->
[![R-CMD-check](https://github.com/vanessaxiaofan/merc/workflows/R-CMD-check/badge.svg)](https://github.com/vanessaxiaofan/merc/actions)
<!-- badges: end -->

The goal of merc is to implement regression calibration methods for validation study and reliability study.

## Installation

You can install the released version of merc from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("merc")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("vanessaxiaofan/merc")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(merc)
## basic example code
# # Only one mismeasured covariate, logistic model
y <- c(1,1,2,3,2,3)
x <- c(2,2.1,3,4,2.9,4.1)
s <- c(2,5,4,3,3,5)
case <- c(0,1,0,1,0,0)
age <- c(10,10,11,12,13,13)
test <- data.frame(y,x,s,case,age)

x <- c(1.1,1.2,0.8)
x2 <- c(1.2,1.2,0.9)
x3 <- c(0.9,1.0,1.3)
relib <- data.frame(x,x2,x3)

wts <- data.frame(x=1,s=1)


### Fit main study logistic model
outModel <- glm(case ~ x + s , family = binomial(link="logit"), data = test)
outcomeParam=coef(outModel)
outcomeParamVCOV=vcov(outModel)
outcomeModelResults<-(list(outcomeParam,outcomeParamVCOV))
Bstar<-outcomeParam[2:length(outcomeParam)] #p' x 1
VBstar<-outcomeParamVCOV[2:length(outcomeParam),2:length(outcomeParam)] # p' x p'

# Provide point estimate
fit1 <- relibpls(supplyEstimates=TRUE, relib=relib, pointEstimates = Bstar, vcovEstimates = VBstar, sur = c("x"), woe = c("s"), weri = c("x","x2","x3"), rr=3, ms=test, weights=wts,link = "logit",method = "glm" )
fit1

# Without point estimate
fit2 <- relibpls(supplyEstimates=FALSE, relib = relib, sur = c("x"), woe = c("s"), weri = c("x","x2","x3"), outcome = c("case"), rr=3, ms=test,method = "glm", family = binomial, link = "logit", weights=wts)
fit2

```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.

